Brownian Dynein Model

### 2015-07-23 latex/derivation.tex
Add rest of angle derivative solutions. Next step: simplify and make numerically computable.

\section{Cartesian from Angular Coordinates}
\begin{align}
  X_{bl} &= 0 \\
  X_{ml} &= X_{bl}+L_{t}\cos(\Theta_{bl}) \\
  X_{t}  &= X_{ml}+L_{s}\cos(\Theta_{ml}) \\
  X_{mr} &= X_{t} +L_{s}\cos(\Theta_{mr}-\pi) \\
  X_{br} &= X_{mr}+L_{t}\cos(\Theta_{br}-\pi) \label{eq:br-definition}
\end{align}

As we found in Eq.~\ref{eq:br-definition}... just kidding!

$$Y_{bl}$$
$$Y_{ml} = Y_{bl}+L_{t}\sin(\Theta_{bl})$$
$$Y_{t}  = Y_{ml}+L_{s}\sin(\Theta_{ml})$$
$$Y_{mr} = Y_{t} +L_{s}\sin(\Theta_{mr}-\pi)$$
$$Y_{br} = Y_{mr}+L_{t}\sin(\Theta_{br}-\pi)$$

\section{Cartesian Velocities}
$$\dot{X}_{bl} = 0$$
$$\dot{X}_{ml} = \dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl}$$
$$\dot{X}_{t } = \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml}$$
$$\dot{X}_{mr} = \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}$$
$$\dot{X}_{br} = \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br}$$

$$\dot{Y}_{bl} = 0$$                                                               
$$\dot{Y}_{ml} = \dot{Y}_{bl} + \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl}$$
$$\dot{Y}_{t}  = \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml}$$
$$\dot{Y}_{mr} = \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}$$
$$\dot{Y}_{br} = \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br}$$

\section{Cartesian Velocities (expanded)}
$$\dot{X}_{bl} = 0$$
$$\dot{X}_{ml} = L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl}$$
$$\dot{X}_{t } = L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml}$$
$$\dot{X}_{mr} = L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}$$
$$\dot{X}_{br} = L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br}$$

$$\dot{Y}_{bl} = 0$$                                                               
$$\dot{Y}_{ml} = \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl}$$
$$\dot{Y}_{t}  = \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml}$$
$$\dot{Y}_{mr} = \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}$$
$$\dot{Y}_{br} = \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br}$$

\section{Brownian Equations}
$$\dot{X}_{bl} = 0$$
$$\dot{X}_{ml} = \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{ls}(X_{ml} - X_{bl}) + \lambda_{lt}(X_{t } - X_{ml}) \Big) + R_{xml}$$
$$\dot{X}_{t } = \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{lt}(X_{t } - X_{ml}) + \lambda_{rt}(X_{mr} - X_{t }) \Big) + R_{xt }$$
$$\dot{X}_{mr} = \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{rt}(X_{mr} - X_{t }) + \lambda_{rs}(X_{br} - X_{mr}) \Big) + R_{xmr}$$
$$\dot{X}_{br} = \frac{1}{\gamma} \Big(F_{xbr} + \mn \lambda_{rs}(X_{br} - X_{mr})                                 \Big) + R_{xbr}$$

$$\dot{Y}_{bl} = 0$$
$$\dot{Y}_{ml} = \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{ls}(Y_{ml} - Y_{bl}) + \lambda_{lt}(Y_{t } - Y_{ml}) \Big) + R_{yml}$$
$$\dot{Y}_{t}  = \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{lt}(Y_{t } - Y_{ml}) + \lambda_{rt}(Y_{mr} - Y_{t }) \Big) + R_{yt }$$
$$\dot{Y}_{mr} = \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{rt}(Y_{mr} - Y_{t }) + \lambda_{rs}(Y_{br} - Y_{mr}) \Big) + R_{ymr}$$
$$\dot{Y}_{br} = \frac{1}{\gamma} \Big(F_{ybr} + \mn \lambda_{rs}(Y_{br} - Y_{mr})                                 \Big) + R_{ybr}$$

@@

$$\dot{X}_{ml} = \dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml}$$
$$\dot{X}_{t} = \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt }$$
$$\dot{X}_{mr} = \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr}$$
$$\dot{X}_{br} = \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr}$$

$$\dot{Y}_{ml} = \dot{Y}_{bl} + \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml}$$
$$\dot{Y}_{t} = \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt }$$
$$\dot{Y}_{mr} = \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr}$$
$$\dot{Y}_{br} = \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr}$$

\section{System after Eliminating $\lambda$s via Addition}

$$
\dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - 
$$
$$
\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl})
$$

$$
\hspace*{-4cm} \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{lt}(X_{t }
$$

$$\dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + 
\dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t })$$

$$\dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr})$$

$$
\hspace{-7cm} \dot{Y}_{bl} + \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl})
$$

$$
\hspace{-4cm} \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml})
$$

$$
\hspace{-2cm} \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t })
$$

$$\dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr})$$

\section{Solution for $\Theta_{br}$}

$$
\hspace{-4cm} \Big (\dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big) \frac{1}{(X_{br} - X_{mr})} = \mn\frac{1}{\gamma}\lambda_{rs} = \Big (\dot{Y}_{mr} - L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big) \frac{1}{(Y_{br} - Y_{mr})}
$$

$$
\hspace{-4cm} \Big (L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr}) = \Big (\mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(X_{br} - X_{mr}) + \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr})
$$

$$
\hspace{-4cm} \Big (L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(X_{br} - X_{mr}) = \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
$$

$$
\hspace{-4cm} \dot{\Theta}_{br} \Bigg(\Big (L_{t}\sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr}) \Bigg ) = \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
$$

$$\dot{\Theta}_{br} = \frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})}{\Big (L_{t}\sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr})}$$
\\

\section{Solution for $\Theta_{mr}$}

>>>>

\section{Cartesian from Angular Coordinates}
\begin{align}
  X_{bl} &= 0 \\
  X_{ml} &= X_{bl}+L_{t}\cos(\Theta_{bl}) \\
  X_{t}  &= X_{ml}+L_{s}\cos(\Theta_{ml}) \\
  X_{mr} &= X_{t} +L_{s}\cos(\Theta_{mr}-\pi) \\
  X_{br} &= X_{mr}+L_{t}\cos(\Theta_{br}-\pi)
\end{align}

\begin{align}
  Y_{bl} &= 0 \\
  Y_{ml} &= Y_{bl}+L_{t}\sin(\Theta_{bl}) \\
  Y_{t}  &= Y_{ml}+L_{s}\sin(\Theta_{ml}) \\
  Y_{mr} &= Y_{t} +L_{s}\sin(\Theta_{mr}-\pi) \\
  Y_{br} &= Y_{mr}+L_{t}\sin(\Theta_{br}-\pi)
\end{align}

\section{Cartesian Velocities}
\begin{align}
  \dot{X}_{bl} &= 0 \\
  \dot{X}_{ml} &= \dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} \\
  \dot{X}_{t } &= \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} \\
  \dot{X}_{mr} &= \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
  \dot{X}_{br} &= \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br}
\end{align}

\begin{align}                                                                          
  \dot{Y}_{bl} &= 0 \\                                                        
  \dot{Y}_{ml} &= \dot{Y}_{bl} + \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl} \\
  \dot{Y}_{t}  &= \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} \\
  \dot{Y}_{mr} &= \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
  \dot{Y}_{br} &= \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br}
\end{align}

\section{Cartesian Velocities (expanded)}
\begin{align}
  \dot{X}_{bl} &= 0 \\
  \dot{X}_{ml} &= L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} \\
  \dot{X}_{t } &= L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} \\
  \dot{X}_{mr} &= L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
  \dot{X}_{br} &= L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br}
\end{align}

\begin{align}                                                                               
  \dot{Y}_{bl} &= 0 \\                                                               
  \dot{Y}_{ml} &= \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} \\
  \dot{Y}_{t}  &= \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml} \\
  \dot{Y}_{mr} &= \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
  \dot{Y}_{br} &= \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br}
\end{align}

  \section{Brownian Equations}
\begin{align}  
  \dot{X}_{bl} &= 0 \\
  \dot{X}_{ml} &= \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{ls}(X_{ml} - X_{bl}) + \lambda_{lt}(X_{t } - X_{ml}) \Big) + R_{xml} \\
  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{lt}(X_{t } - X_{ml}) + \lambda_{rt}(X_{mr} - X_{t }) \Big) + R_{xt } \\
  \dot{X}_{mr} &= \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{rt}(X_{mr} - X_{t }) + \lambda_{rs}(X_{br} - X_{mr}) \Big) + R_{xmr} \\
  \dot{X}_{br} &= \frac{1}{\gamma} \Big(F_{xbr} + \mn \lambda_{rs}(X_{br} - X_{mr})                                 \Big) + R_{xbr}
\end{align}

\begin{align}  
  \dot{Y}_{bl} &= 0 \\
  \dot{Y}_{ml} &= \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{ls}(Y_{ml} - Y_{bl}) + \lambda_{lt}(Y_{t } - Y_{ml}) \Big) + R_{yml} \\
  \dot{Y}_{t}  &= \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{lt}(Y_{t } - Y_{ml}) + \lambda_{rt}(Y_{mr} - Y_{t }) \Big) + R_{yt } \\
  \dot{Y}_{mr} &= \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{rt}(Y_{mr} - Y_{t }) + \lambda_{rs}(Y_{br} - Y_{mr}) \Big) + R_{ymr} \\
  \dot{Y}_{br} &= \frac{1}{\gamma} \Big(F_{ybr} + \mn \lambda_{rs}(Y_{br} - Y_{mr})                                 \Big) + R_{ybr}
\end{align}

@@

\begin{align}  
  \dot{X}_{ml} &= \dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml} \\
  \dot{X}_{t}  &= \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt } \\
  \dot{X}_{mr} &= \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr} \\
  \dot{X}_{br} &= \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr}
\end{align}

\begin{align}  
  \dot{Y}_{ml} &= \dot{Y}_{bl} + \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml} \\
  \dot{Y}_{t}  &= \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt } \\
  \dot{Y}_{mr} &= \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr} \\
  \dot{Y}_{br} &= \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr}
\end{align}

\section{System after Addition to simplify RHS}

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) =
\dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{s}\sin(\Theta_{ml}) \dot{\Theta}_{ml} - R_{xt } \\
- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr}
-\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\end{multline}

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) =
\dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\end{multline}

\begin{equation}
\mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) =
\dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
+ \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\end{equation}

\begin{equation}
\mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) = 
\dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\end{equation}

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) =
\dot{Y}_{bl} + \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml}) \dot{\Theta}_{ml} \\
- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
+ \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
\end{multline}

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) =
\dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
\end{multline}

\begin{equation}
\mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) =
\dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br}
- R_{ybr} - \frac{1}{\gamma}F_{ybr}
\end{equation}

\begin{equation}
\mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) = \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
\end{equation}

\section{Solution for $\dot{\Theta_{br}}$}

\begin{multline}
\Big (\dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big) \frac{1}{(X_{br} - X_{mr})} = \mn\frac{1}{\gamma}\lambda_{rs}
= \Big (\dot{Y}_{mr} - L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big) \frac{1}{(Y_{br} - Y_{mr})}
\end{multline}

\begin{multline}
\Big (L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
= \Big (\mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(X_{br} - X_{mr}) + \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr})
\end{multline}

\begin{multline}
\Big (L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(X_{br} - X_{mr})
= \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
\end{multline}

\begin{multline}
\dot{\Theta}_{br} \Bigg(\Big (L_{t}\sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr}) \Bigg )
= \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
\end{multline}

\begin{equation}
\dot{\Theta}_{br} = \frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} 
- R_{xbr} \Big)(Y_{br} - Y_{mr})}{\Big (L_{t}\sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr})}
\end{equation}
